\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-09-07 paper.tex
Modify Component - MAM

\maketitle
\section*{\normalsize\textbf{Abstract}}
Data as a Service (DaaS) offers consumption data, geographic information, etc., for a number of years and has come to form a multi-billion dollar industry. But IoT cannot be considered a mere extension of DaaS. Transacting IoT data must be different in many respects in order to build much-needed trust in IoT-enabled Data Marketplaces, trust that will be key to their sustainability. Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making.

In this paper, we propose a novel approach to construct IoT-enabled data marketplace by means of decentralized and trustless architecture, putting not merely the trading records but also the transaction process on the distributed ledgers. This way can efficiently enhance the degree of transparency, since all interactions with smart contracts will be written on-chain. In other words, users transport the encrypted data audited by smart contracts for storage via an end-to-end encrypted message channel which allows emitting and accessing trusted data stream over the distributed ledger regardless of the size or cost of device, simultaneously making a verifiable Auth-compliant request to the platform. Later, the verified data will enter data marketplace to be traded. Furthermore, the platform will complete matching, trading and refunding without human intervention in the whole process, and also protect the rights of data providers and consumers through trading policy written on smart contract, and finally apply evolutionary game theory to machine economy.

@@

The utility structure of IoT econimic system and game theory models are evaluated by Dusit Niyato et al.\cite{UtilityStruct}. Game theory provides a mathematical solution to proof the existence of Nash Equilibrium in IoT economy. The authors ensures the sustainability of IoT economy by game theory. Data marketplace organizers can apply numerical analysis on game theory, which would help them to find out their optimal pofit. However, few things didn't be mentioned in their work including refund and subscription economy.

The previous work proposed different solution to specific issues of data marketplace. In this paper, we proposed an  overall design of decentralized data markeplace that takes care of data integrity and trading procedure such as buyout and subsciption on distributed ledger.

@@

\subsubsection{Registrar}
Registrar is responsible for creating a Registration Contract, which maintains a lookup table of participants, and adding new data providers, consumers and brokers to the decentralized data marketplace.

\subsubsection{Data Provider}
Data providers, who generate and preserve streaming data, are willing to sell streaming data to consumers. They decide the subscription period, subscription price, data type, sampling frequency. Afterward, they can launch the product on the decentralized data marketplace. Next, they collect raw data and send to the broker who assists in uploading data to the network. An MAM channel\cite{MAM} is used to store encrypted data stream. They receive subscription fees from consumers, which can be used to improve the quantity and accuracy of their device or service.

\subsubsection{Consumer}
Consumers aspire to obtain streaming data to promote the value of their service. However, it is a big challenge for most consumers to collect the desired data by themselves. So they look forward to purchasing the streaming data from data providers. They search products on the marketplace and pay for subscription fee. While the payment is received, the smart contract adds the consumer to the consumers lists of that product automatically. The session key would be exchanged and consumers can decrypt the ciphertext on the MAM channel, which contains streaming data.

\subsubsection{Broker}
Brokers represent data providers and consumers to do computing tasks in the DLT (Distributed Ledger Technology) since brokers are expected to have high computing power. Once a data provider wants to launch a new product, the data provider requests a broker to create a new MAM channel, a new Product Contract, which specifies details about products, and upload this product to a decentralized storage system\cite{IPFS}. Also the broker certifies the session key which is used for symmetric encryption for streaming data encryption and decryption. Then the broker provides the matching service for data provider’s products and consumer’s queries. After that, the broker is requested to deal with the trading process and upload the provider’s data streams to the MAM channel. For each products, brokerage fees will be charged by the broker.

@@

However, MAM resolves this problem, it is a second layer data communication protocol enables to emit and access an encrypted data stream over Tangle network and ensures data integrity.
It publishes each message to different addresses that each can be derived from the previous one, this forms a MAM channel. Furthermore, a session key can be provided to control the visibility and access to a MAM channel.

@@

Data provider would receive subscription fee for buying data each time the data is transmitted to consumer; unpaid subscription fee would be stored in smart contract. The consumer will keep buying data from data povider, only when the data sold by the data provider with high enough accuracy, which we called these data as decent data.
Once the accuracy is lower than a certain accuracy, which we called it as unacceptable data, the consumers would consider this data provider as a low quality data provider, and reject to buy the data from this data provider.

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contract (Figure \ref{fig:registration_contract}), which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys. Only one Registration Contract is needed, and everyone can query the participants' public keys. Then some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace. Anyone who would like to sell or purchase data may register to become the data providers or consumers. The registrar has the authority to agree with applications. After that, their identities are available in the Registration Contract and launching and trading processes can be started.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\textwidth]{registration_contract}
    \caption{Registration Contract.}
    \label{fig:registration_contract}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{launching_product}
    \caption{The process of launching a product.}
    \label{fig:launching_product}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\textwidth]{product_contract}
    \caption{Product Contract.}
    \label{fig:product_contract}
\end{figure}

To sell the streaming data, a data provider has to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}. The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract (Figure \ref{fig:product_contract}). Each product has a Product Contract to record the trading process.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{trading_product}
    \caption{The process of the product trading.}
    \label{fig:trading_product}
\end{figure}

@@

The whole trading process is shown in Figure \ref{fig:trading_product}. Once a consumer who want to subscribe the streaming data pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract. To decrypt the streaming data on the MAM channel, session key $k$ should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.

The data provider requests the consumers list maintained by the Product Contract and obtains accounts of each consumer. After that, the data provider can also get public keys of each consumer from the Registration Contract with their accounts. For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the Product Contract. Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key $k$ and signature $Sign(k)$.

@@

\subsection{Game Theory Evaluation}
\subsubsection{Repeated Game}
Repeated game consists of serveral repetitions of some stage games. In each stage game, the action player takes will effect the actions that players are going to take in the future stages. Repeated game can be illustrated with a decision tree and described their payoff with discounted sum of payoff. Discounted sum of payoff can capture the idea that what the players truly pursue is the sum of payoff in all stages and payoff in different stages may varify.

\subsubsection{Model Description}
We use a repeated game to express the scenario of our Data Marketplace. Figure.\ref{fig:decision_tree} shows the decision tree to depict the the repeated game we used. Each level in this decision tree represents each round of data transmission from data provider to consumers, and the consumers would pay subscription fee, $p_s$, each person. The sum of all the subscription fee pays to data provider is denoted as $P_s$.

Refund is a major issue in our research. However, we don't have to take refund as a factor in our repeated game, since in our decentralized data marketplace we use smart contract to store the subscription fee which will be paid to buy the future data. The subscription fee will be paid as data provider provides new data. In other words, data provide doesn't need to take any procedure to transer subscription fee from his/her own account to consumers' account. For the same reason, data provider has no responsibility on the refunding processing fee charged by the smart contract as well.

@@

We have these following assumptions:
\begin{itemize}
    \item  There is no any other data providers provide the same product in Data Marketplace. Therefore, we can consider each provider's behavior independently. That means this decision tree represent the behavior of only one data provider.
    \item  More than 51\% of consumers are among complete information exchange state. In other words, once one of them launches voting for stopping buying data and refunding, they would succeed in refund voting.
    \item  One of the consumers who has complete information exchange with other 51\% buyers has the ability to examine the data quality. If unacceptably low accuracy data are delivered to consumers, this examiner will spread this information out.
\end{itemize}

Based on the description above, the discounted sum of payoff for our repeated game is
\begin{equation} \label{payoff}
    \sum_{i=0}^{m}{\beta^{in}\cdot [(\sum_{j=0}^{n} \beta^j \cdot P_s) - C_{maintain}]}
\end{equation}

\begin{itemize}
    \item $P_s$ is the sum of subscription price (fee) for all subscriber.
    \item $C_{maintain}$ is the cost of sensor maintenance in $n$ round.
    \item $\beta$ is discounted factor.
    \item $n$ is how many round for one maintenance period.
    \item $m$ is how many maintenance periods have been experienced in this repeated game.
\end{itemize}

Al-Fagih et al. presented\cite{DataPrice} $P_s$ is a sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is about a exponential function of $P_r$. We can substitute $P_s$ and $C_{maintain}$ with $P_r$ into Eq. (\ref{payoff}), then we can find out the Nash Equilibrium of repeated game easily.

>>>>

\maketitle
\section*{\normalsize\textbf{Abstract}}
Data as a Service (DaaS) has been offering consumption data, geographic information, etc., for a number of years and has evolved into a multi-billion dollar industry. But IoT cannot be considered a mere extension of DaaS. Transacting IoT data must be different in many respects in order to build much-needed trust in IoT-enabled data marketplaces, trust that will be key to their sustainability. Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making.

In this paper, we propose a novel approach to construct IoT-enabled data marketplace by means of decentralized and trustless architecture, posting the trade records but also including the transaction process on the distributed ledgers. This way can efficiently enhance the degree of transparency, since all interactions with smart contracts will be written on-chain. In other words, users transport the encrypted data audited by smart contracts for storage via an end-to-end encrypted message channel which allows emitting and accessing trusted data stream over the distributed ledger regardless of the size or cost of the device, simultaneously making a verifiable Auth-compliant request to the platform. Later, the verified data will enter the data marketplace to be traded. Furthermore, the platform will complete matching, trading and refunding process without the human intervention which also protects the rights of data providers and consumers through a trading policy written on the smart contract, and finally apply evolutionary game theory to the machine economy.

@@

The sustainability of IoT economic system is under discussion by Dusit Niyato et al.\cite{UtilityStruct}. They evaluated the utility structure of data trading and presented game theory model with the utility structure which provides a way to find out the Nash Equilibrium. The existence of Nash Equilibrium can help us to determine if the policy of the decentralized data marketplace can ensure a sustainable system. However, few things didn't be mentioned in their work including refund and subscription economy.

The previous work proposed different solution to specific issues of data marketplace. In this paper, we proposed an  overall design of decentralized data marketplace that takes care of data integrity and trading procedure such as buyout and subsciption on distributed ledger.

@@

\subsubsection{Registrar}
The registrar is responsible for creating a Registration Contract, which maintains a lookup table of participants, and has the authority to control the participant lists of the decentralized data marketplace.

\subsubsection{Data Provider}
Data providers, who generate and preserve streaming data, are willing to sell streaming data to consumers. They can launch the product on the decentralized data marketplace and receive subscription fees from consumers, which can be used to improve the quantity and accuracy of their device or service.

\subsubsection{Consumer}
Consumers aspire to obtain streaming data to promote the value of their service. However, it is a big challenge for most consumers to collect the desired data by themselves. So they look forward to purchasing the streaming data from data providers.

\subsubsection{Broker}
Brokers represent data providers and consumers to do computing tasks in the DLT (Distributed Ledger Technology) since brokers are expected to have high computing power. Once a data provider wants to launch a new product, the broker is requested to deal with the trading process and upload the provider’s data streams to the MAM channel. For each products, brokerage fees will be charged by the broker.

@@

However, MAM resolves this problem, it publishes messages to \textbf{channel}, which is a form of transactions that each address can be derived from the previous one. One can create multiple channels as possible, however, the size of a channel is fixed which is decided before creation, the more messages one wants to send in a channel, the more computation power is needed during creation. Thus data providers should decide how to distribute product into MAM channel by evaluating the cost. Furthermore, a session key can be provided to control the visibility and access to the data on MAM channel.

@@

The consumer will pay for the data, only when the data sold by the data provider with high enough quality/accuracy, which we called these data as decent data.
Once the accuracy is lower than a certain threshold, which we called these data as unacceptable data, the consumers would consider this data provider as a low quality data provider, and stop buying data from this data provider.

Refund is a major issue in our research. However, we don't have to take refund as a factor in our game theory model, since in our decentralized data marketplace we use smart contract to store the subscription fee which will be paid to buy the future data. The subscription fee will be paid as new data is transmitted to consumers. In other words, data provider doesn't need to take any procedure to transfer subscription fee from his/her own account to consumers' account. For the same reason, data provider has no responsibility on the refunding processing fee charged by the smart contract as well.

\subsection{Participants Registration}
At the beginning, the registrar creates a Registration Contract, which maintains all participants' information, including their DID (Decentralized Identifiers) Documents and public keys. Only one Registration Contract is needed, and everyone can query the participants' public keys. Then some trustworthy brokers who pass procedures for conformity assessment are added to the decentralized data marketplace. Anyone who would like to sell or purchase data may register to become the data providers or consumers. The registrar has the authority to agree with applications. After that, their identities are available in the Registration Contract and launching and trading processes can be started.

@@

To sell the streaming data, a data provider has to launch a new product on the data marketplace in advance as shown in Figure \ref{fig:launching_product}. The data provider determines a trusted broker and asks the broker to create a new MAM channel and Product Contract. Each product has a Product Contract to record the participants, subscription price brokerage fee, quantity of data and  trading process.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.4\textwidth]{launching_product}
	\caption{The process of launching a product.}
	\label{fig:launching_product}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\textwidth]{trading_product}
    \caption{The process of the product trading.}
    \label{fig:trading_product}
\end{figure}

@@

The whole trading process is shown in Figure \ref{fig:trading_product}. Once a consumer who wants to subscribe the streaming data pays a subscription fee to the Product Contract, it is added to the consumers list automatically by the smart contract. Next, session key $k$ should be exchanged between data provider and consumers as shown in Figure \ref{fig:key_exchange}.

The data provider can obtain public keys of each consumer from the Registration Contract. For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the Product Contract. Consumers listen to the smart contract event which is triggered when the ciphertext is updated, and decrypt the ciphertext to get the session key $k$ and signature $Sign(k)$.

@@

On the other hand, we would consider the situation that one of the consumers requests a refund in our future work. When the consumer is disappointed with the data quality, it may request a refund. Its permit should be cancelled while other consumers are unaffected.

\subsection{Game Theory Evaluation}
Game Theory is a methodology to discuss strategic interaciton among game players. If we can ensure Nash Equilibrium of decentralized data marketplace exists at certain acceptable range, then we can promise the sustainability of decentralized data marketplace. Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied on data pricing. To describe the scenario more precisely, we decided to use repeated game to build our game theory model which meets the scenario of subscription economy more.

Figure.\ref{fig:decision_tree} shows the decision tree to depict the the repeated game we used. Each level in this decision tree represents each round of data transmission from data provider to consumers, and the consumers would pay subscription fee, $p_s$, each person. The sum of all the subscription fee pays to data provider is denoted as $P_s$.

@@

We have these following assumptions:
\begin{itemize}
    \item  There is no any other data providers provide the same product in Data Marketplace. Therefore, we can consider each provider's behavior independently. That means this decision tree represent the behavior of only one data provider.
    \item  More than 51\% of consumers are among complete information exchange state. In other words, once one of them launches voting for stopping buying data and refunding, they would succeed in refund voting.
    \item  One of the consumers who has complete information exchange with other 51\% buyers has the ability to examine the data quality. If unacceptably low accuracy data are delivered to consumers, this examiner will spread this information out.
    \item  We assume the number of dishonest consumers is really small, so it can be negleted.
\end{itemize}

Based on the description above, the discounted sum of payoff for our repeated game is
\begin{equation} \label{payoff}
    \sum_{i=0}^{m - 1}{\beta^{in}\cdot [(\sum_{j=0}^{n - 1} \beta^j \cdot P_s) - C_{maintain}]}
\end{equation}

Al-Fagih et al. presented\cite{DataPrice} $P_s$ is sigmoid function of $P_r$, and based on rule of thumb $C_{maintain}$ is about a exponential function of $P_r$. We can substitute $P_s$ and $C_{maintain}$ with $P_r$ into Eq. (\ref{payoff}), then we can find out the Nash Equilibrium of repeated game. We will discuss more in the next section.

\subsubsection{Numerical Example}
To evaluate the behavior of the model we presented, first, we would express the function of $P_s$ and $C_{maintain}$ as function of $P_r$ respectively. Therefore, the sum of subscription fee of all subscriber can be expressed as

\begin{equation} \label{sub_fee}
P_s = R \frac{e^{a (P_r - b)}}{1 + e^{a (P_r - b)}}
\end{equation}

where $a$ and $b$ are tuning factors, and $R$ is the maximun data value.
And we would express the cost of maintenance as

\begin{equation} \label{C_mtn}
C_{maintain} = ce^{P_r - d}
\end{equation}
Where $c$ and $d$ is tuning factor.

Substitute Eq. (\ref{sub_fee}) and Eq. (\ref{C_mtn}) into Eq. (\ref{payoff}). We can derive
\begin{equation} \label{payoff_Pr}
\sum_{i=0}^{m - 1}{\beta^{in}\cdot [(\sum_{j=0}^{n - 1} \beta^j \cdot R \frac{e^{a (P_r - b)}}{1 + e^{a (P_r - b)}}) - ce^{P_r - d}]}
\end{equation}

Let tuning factors $, a = 0.15, b = 50, R = 10000, c = 1, d = 88$, and there is only one maintenance period has happened and one maintenance period consists of 12 rounds which means $m = 1, n = 12$. Based on these parameters, we can plot the payoff function as function of accuracy, $Pr$ which is Figure.\ref{fig:payoff_pic}. The maximun point occurs at $accuracy \approx 92\%$ which we point it out with red dot.
\begin{figure} \centering \includegraphics[width=3.3in]{payoff_pic} \caption{Payoff Function}
    \label{fig:payoff_pic} \end{figure}

Figure.\ref{fig:payoff_pic} illustratres the market mechanism of the subscription trading policy we used under the decentralized data marketplace. First, data providers have weak motivation to operate their sensor in low accuracy, since the incentive of low quality data is mush less than moderate quality data. Second the great deficit at high accuracy is mostly drived by the rapid increasing of maintenance cost. Thus, if the maintenance fee to achieve decent data quality is under a fair price range, then data provider will automatically provide data with high enough data quality under our assumptions.
